% To check in final format
%\documentclass[final,twocolumn]{elsarticle}
\documentclass[preprint,review,12pt]{elsarticle}

\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage[noend]{algpseudocode}
\usepackage{subfig}
\usepackage[table,xcdraw]{xcolor}
\usepackage{amsthm}
\usepackage{color}
\usepackage{soul}
\usepackage{ulem}
\usepackage{amsmath}
\usepackage{float}

\newcommand{\hlr}[2][red]{
  {\sethlcolor{#1} \hl{#2}}
}

\newcommand{\hly}[2][yellow]{
  {\sethlcolor{#1} \hl{#2}}
}
\newcommand{\hlg}[2][green]{
  {\sethlcolor{#1} \hl{#2}}
}
\newcommand{\hlp}[2][pink]{
  {\sethlcolor{#1} \hl{#2}}
}

\usepackage{lineno,hyperref}
\modulolinenumbers[5]

\journal{Journal of \LaTeX\ Templates}

\bibliographystyle{elsarticle-num}

\begin{document}

\begin{frontmatter}

\title{Joint Service Chain Deployment and Manager Placement in NFV}

\author[aut]{Parham Alvani}
\ead{parham.alvani@aut.ac.ir}

\author[aut]{Bahador Bakhshi
\corref{correspondingauthor}}
\ead{bbakhshi@aut.ac.ir}

\cortext[correspondingauthor]{Corresponding author.}

\address[aut]{Amirkabir University of Technology, Tehran, Iran}

\begin{abstract}
\hly{%
a) Motivation \\
b) Introduce the problem \\
c) Why is there a research gap \\
d) What have we done \\
e) What are the results \\
}

In the old times, Network providers use physical network functions to create their service chains, but a change in this manner is difficult and may cause many service disruption.
SFC and NFV is the solution to this difficulty. By using SFC and NFV, providers can provision chains dynamically and then change them in run time.
One of the main requirements is management and monitoring for the chains.
In this research, we consider the chain acceptance problem subject to management resources. In the first step, we formulate
problem with ILP and then implement it in CPLEX framework. As we know, ILP problems are NP-Hard, so we need a Polynomial-Time solution to the problem.
In this research, we develop a heuristic algorithm and compare its result with the optimal solution. In the end, the heuristic solution produces near-optimal results in the polynomial time.
\end{abstract}

\begin{keyword}
\end{keyword}

\end{frontmatter}

\section{Introduction}
\hly{%
a) A general introduction of the context \\
b) More specific context of problem and its importance \\
c) A very brief review of literature and introduce the research gap \\
d) What is the problem \\
e) What are the contributions \\
f) The structure of the paper \\
}
\input{introduction}


\section{Related Work}\label{sec:related-works}
\input{related-works}

\section{System Model and Problem Statement}\label{sec:system-model}
\input{system}

\section{Problem Formulation}\label{sec:formulation}
\input{formulation}

\section{Proposed Solution}\label{sec:solution}
\input{solution}

\section{Evaluation and Numerical Results}\label{sec:results}
\hly{
a) Simulation settings: Topologies and all other parameters used in simulation it is better to use a table \\
The algorithms which are simulated \\
Parameters used for evaluation \\
b) A subsection per parameter\\
Emphasize on achievements\\
}
\input{results}

\section{Conclusion and Future Work}\label{sec:conclusion}
\hly{
a) Review of what we have done \\
b) What is the future step \\
}

\bibliography{references}

\end{document}
