We have formulated the JSD-MP problem in ILP and its optimal solution requires NP-Hard.
In this section we represent a way to have a near-optimal solution in polynomial time.
In reality providers need to decide quickly for their SFC request and the later solution will help them.
As we mentioned before JSD-MP problem consists of two parts that we formulate together.
First part is VNF placement and the second part is VNFM placement.

\subsection{Maximizing the Accepted SFC Requests with Management Constraints (MASMAN)}
For each chain we devide the placement into two different phase that are solved using different algorithms.
The first phase is the VNF placement phase that we are solve it with Bari \cite{Bari2015} algorithm.
This algorithm is an efficient algorithm for SFC placement that can be used here but it doesn't consider the management resources.
This algorithm for each chain solves a Dynamic Programming problem and decide each node location with its previous one to minimize the cost term.
Here we add a new stage to this algorithm to decide the VNFM at the last. By this way we also consider the management resources jointly with SFC placement.
At the end, we used Tabu Search for improving the VNFM placement. By improving we mean merging VNFM to reduce the license cost.

%% TODO: Add algorithm pseudocode

\cite{AbuLebdeh2017} considers the VNF placement is know a prior so we must used its algorithm after the VNF placement.
Therefore, to comparing MASMAN with \cite{AbuLebdeh2017} as the nearest work to JSD-MP,
We use the Bari \cite{Bari2015} algorithm for the placement and then use the proposed way in the \cite{AbuLebdeh2017} for VNFM placement.
The proposed way in \cite{AbuLebdeh2017} use Tabu Search for finding the best VNFM placement.
The results of this comparasion are availabe at the following sections.

%% Complexity analysis